[dcpo_demsupport]

### 2020-08-26 paper/dcpo_demsupport.Rmd
fixed #12

df_thetaDraw <- map_df(seq(claassen_m5_theta$theta[1, , 1]),
       function(year) {
         map_df(seq(claassen_m5_theta$theta[1, 1, ]),
                function(country) {
                  df_temp <-
                    sample(claassen_m5_theta$theta[, year, country],
                           size = 100,
                           replace = TRUE) %>%
                    matrix(ncol = 100) %>%
                    as_tibble()
                  df_temp$yearID <- year
                  df_temp$countryID <- country
                  return(df_temp)
                })
       }) %>% 
  pivot_longer(
    df_temp,
    cols = starts_with("V"),
    names_to = "draw",
    values_to = "theta"
  ) %>% 
  group_split(draw)
```

@@

df_result_cls <- map(ls_mod, function(mod){
  result <- plm(ls_mod, model = "pooling", data = sd.plm)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result))
})

# GMM ----

## Windmeijer corrected standard errors
vcovHC_se <- function(x) {
  plm::vcovHC(x) %>% 
    diag() %>% 
    sqrt()
}

ls_mod <- 
  paste0(
    "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
    c(
      "plm::lag(SupDem_trim, 1)",
      "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)"
    ),
    "+ plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)",
    " | plm::lag(Libdem_VD, 3:5)"
  )

df_result_cls[3:4] <- map(ls_mod, function(mod){
  result <- pgmm(as.formula(ls_mod), effect="individual", model="onestep", transformation="ld", indexes=c("Country", "Year"), data = sd.plm)
  df_result <- coef(result) %>% 
    tibble::enframe(name = "term", value = "estimate") %>% 
    mutate(std.error = vcovHC_se(result))
})

@@

```{r dcpo-uncertainty, eval = FALSE}

# Data input ----
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_sigma.rda"))
load(here::here("data", "dcpo_theta.rda"))

df_controls <- read_csv(here::here("data", "control_variables.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"),
         regime = Vdem_libdem > 1)

@@

df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

mod_ls <- paste0(
  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(sigma, 1) + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
)

@@

mod_ls <- paste0(
  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(sigma, 1) + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)",
    " | plm::lag(Vdem_libdem, 3:5)"
)

df_result_dcpo[3] <- map(mod_ls[[1]], estimate_dcpo, aType = "gmm")

# df_result_dcpo[4] <- map(mod_ls[[2]], estimate_dcpo, aType = "gmm")

@@

```{r polarizationVisualization, fig.cap="Variance of Polarization"}
# Bootstrap to get confidence intervals----

## function to obtain the mean
Bmean <- function(data, indices) {
  d <- data[indices] # allows boot to select sample 
    return(mean(d))
}

## bootstrapping with 1000 replications 
bootstrapCI_sigma <- function(aData) {
  aSigma <- aData$sigma
  result_temp <- boot(data = aSigma,
                      statistic = Bmean,
                      R = 1000) %>%
    boot.ci(type = "bca")
  tibble(
    mean = mean(aSigma),
    conf.low = result_temp$bca[4],
    conf.high = result_temp$bca[5]
  )
}

df_sigma <- purrr::map(1:1000, function(anEntry) {
  dcpo_sigma$sigma[anEntry, , ] %>%
  reformat_dcpo_output("sigma")
})

df_sigma_us <- map_df(df_sigma, function(aCountry){
  filter(aCountry, country == "United States")
})

df_sigma_usCI <- map_df(unique(df_sigma_us$year), function(aYear){
  dataAYear <- filter(df_sigma_us, year == aYear)
  bootstrapCI_sigma(dataAYear)
}) %>% 
  mutate(year = unique(df_sigma_us$year))

df_sigma_2019 <- map_df(df_sigma, function(aCountry){
  filter(aCountry, year == 2019)
})

df_sigma_2019CI <- map_df(unique(df_sigma_2019$country), function(aCountry){
  dataACountry <- filter(df_sigma_2019, country == aCountry)
  bootstrapCI_sigma(dataACountry)
}) %>% 
  mutate(country = unique(df_sigma_2019$country))

plot_us <- ggplot(df_sigma_usCI, aes(x = mean, y = year, xmin = conf.low, xmax = conf.high)) +
  geom_point() +
  geom_errorbarh(height=.2) + 
  scale_y_reverse(breaks = unique(df_sigma_us$year)) +
  xlab(expression("Polarization Estimates, "~sigma)) + 
  ggtitle("Polarization of the U.S. from 1988--2020") +
  theme_minimal() +
  theme(axis.title.y = element_blank())

plot_2019 <- ggplot(df_sigma_2019CI, aes(x = mean, y = country, xmin = conf.low, xmax = conf.high)) +
  geom_point() +
  geom_errorbarh(height=.2) + 
  xlab(expression("Polarization Estimates, "~sigma)) + 
  ggtitle("Polarization around the World in 2019") +
  theme_minimal() +
  theme(axis.title.y = element_blank())

gridExtra::grid.arrange(plot_us, plot_2019, nrow = 1)
```

```{r dcpoVisualization, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}

load(here::here("output", "estimates_dcpo.RDS"))
load(here::here("output", "estimates_cls.RDS"))

df_plot <- df_result_cls[[1]] %>% 
  mutate(model = "Uncertainty\n Ignored",
         type = "Pooled OLS")

df_plot <- df_result_dcpo[[1]] %>% 
  mutate(model = "DCPO",
         type = "Pooled OLS") %>% 
  rename(std.error = se) %>% 
  bind_rows(df_plot)

df_plot <- df_result_cls[[3]] %>% 
  mutate(model = "Uncertainty\n Ignored",
         type = "System GMM") %>% 
  bind_rows(df_plot)

df_plot <- df_result_dcpo[[3]] %>% 
  mutate(model = "DCPO",
         type = "System GMM") %>% 
  rename(std.error = se) %>% 
  bind_rows(df_plot) %>% 
  select(term, estimate, std.error, model, type)

@@

plot_pooled <- filter(df_plot, type == "Pooled OLS") %>% 
  dwplot(by_2sd = FALSE) %>% 
  relabel_predictors(
    c(
`plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
`plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
`plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
`plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
`plm::lag(theta, 1)` = "Democratic Mood(t-1)",
`plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
`plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
`plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
`plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
`plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
`plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
`plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
`plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
`plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
`plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)",
`plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("Pooled OLS") +
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank(),
        legend.position = "none")

plot_gmm <- filter(df_plot, type == "System GMM") %>% 
  dwplot(by_2sd = FALSE) %>% 
  relabel_predictors(
    c(
`plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
`plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
`plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
`plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
`plm::lag(theta, 1)` = "Democratic Mood(t-1)",
`plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
`plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
`plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
`plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
`plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
`plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
`plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
`plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
`plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
`plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)",
`plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("System GMM") +
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        legend.title = element_blank())

gridExtra::grid.arrange(plot_pooled, plot_gmm, ncol = 2)
```

>>>>

df_thetaDraw <- map_df(seq(claassen_m5_theta$theta[1, , 1]),
       function(year) {
         map_df(seq(claassen_m5_theta$theta[1, 1, ]),
                function(country) {
                  df_temp <-
                    sample(claassen_m5_theta$theta[, year, country],
                           size = 100,
                           replace = TRUE) %>%
                    matrix(ncol = 100) %>%
                    as_tibble()
                  df_temp$yearID <- year
                  df_temp$countryID <- country
                  return(df_temp)
                })
       }) %>% 
  pivot_longer(
    cols = starts_with("V"),
    names_to = "draw",
    values_to = "theta"
  ) %>% 
  group_split(draw)
```

@@

df_result_cls <- map(ls_mod, function(mod){
  result <- plm(mod, model = "pooling", data = sd.plm)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result))
})

@@

```{r dcpo-point}
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_theta.rda"))
load(here::here("data", "dcpo_sigma.rda"))

df_controls <- read_csv(here::here("data", "control_variables.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"),
         regime = Vdem_regime > 1)

@@

df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country"))
}) %>% 
  group_by(country, year) %>% 
  summarise(theta = mean(theta), 
            sigma = mean(sigma))

df_dcpoMean <- df_dcpoMean %>% 
  left_join(df_controls, by = c("country", "year")) %>% 
  mutate(theta_dem = theta * regime,
         theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))

ls_mod <- paste0(
  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
)

df_result_dcpoMean <- map(ls_mod, function(mod){
  result <- plm(mod, model = "pooling", data = df_dcpoMean)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result))
})

save(df_result_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
```

```{r dcpo-uncertainty, eval = FALSE}
df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

mod_ls <- paste0(
  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
)

@@

@@

```{r visualizedMood, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}

load(here::here("output", "estimates_cls.RDS"))
load(here::here("output", "estimates_dcpoMean.RDS"))
load(here::here("output", "estimates_dcpo.RDS"))

df_plot <- df_result_cls[[1]] %>% 
  mutate(model = "Claassen 2019")

df_plot <- df_result_dcpoMean[[1]] %>% 
  mutate(model = "DCPO\n (Point Estimates)") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Democratic\n Mood\n (t-1)",
      "Log GDP\n per capita\n (t−1)",
      "GDP per\n capita Growth\n (t−1)",
      "Regional\n Democracy\n (t−1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n Dependence\n (t−1)"),
    time = 2)
  )

@@

plot_clsVsDCPO <- small_multiple(df_plotS) +
  theme_minimal() +
  ggtitle("DV: Liberal Democracy (Vdem)")+
  theme(legend.position = "none")

df_plot <- df_result_cls[[2]] %>% 
  mutate(model = "Claassen 2019")

df_plot <- df_result_dcpoMean[[2]] %>% 
  mutate(model = "DCPO\n (Point Estimates)") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Democratic\n Demo Only\n (t-1)",
      "Democratic\n Auto Only\n (t-1)",
      "Log GDP\n per capita\n (t−1)",
      "GDP per\n capita Growth\n (t−1)",
      "Regional\n Democracy\n (t−1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n Dependence\n (t−1)"),
    time = 2)
  )

plot_clsVsDCPO2 <- small_multiple(df_plotS) +
  theme_minimal() +
  ggtitle("DV: Liberal Democracy (Vdem)")+
  theme(legend.position = "none")

gridExtra::grid.arrange(plot_clsVsDCPO, plot_clsVsDCPO2, ncol = 2)
```

```{r visualizedSep, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}

df_plot <- df_result_dcpoMean[[1]] %>% 
  mutate(model = "DCPO\n (Point Estimates)")

df_plot <- df_result_dcpo[[1]] %>%
  mutate(model = "DCPO\n (w. Uncertainty)") %>%
  rename(std.error = se) %>%
  bind_rows(df_plot)

plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
  dwplot(by_2sd = FALSE) %>%
  relabel_predictors(
    c(
      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
      `plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
      `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
      `plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
      `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
      `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
      `plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
      `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
      `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("DV: Liberal Democracy (Vdem)") +
  xlab("Coefficient Estimate") +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank()
  )

df_plot <- df_result_dcpoMean[[2]] %>% 
  mutate(model = "DCPO\n (Point Estimates)")

df_plot <- df_result_dcpo[[2]] %>%
  mutate(model = "DCPO\n (w. Uncertainty)") %>%
  rename(std.error = se) %>%
  bind_rows(df_plot)

plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
  dwplot(by_2sd = FALSE) %>%
  relabel_predictors(
    c(
      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
      `plm::lag(theta_dem, 1)` = "Mood Democracy(t-1)",
      `plm::lag(theta_aut, 1)` = "Mood Autocracy(t-1)",
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("DV: Liberal Democracy (Vdem)") +
  xlab("Coefficient Estimate") +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank()
  )

gridExtra::grid.arrange(plot_pooled,plot_pooled2, ncol = 2)
```
